\chapter*{Acknowledgments}

I would like to express my deep appreciation to the individuals who have played 
pivotal roles leading to the successful completion of my PhD dissertation. 
Their support, encouragement, and guidance have been instrumental in 
shaping my academic journey.
First and foremost, I am grateful to my advisor Jamie Oaks for his 
generosity, kindness, and mentorship throughout my time at Auburn. 
You have been a wonderful teacher and a fantastic role model. 
I would also like to thank my committee member Laurie Stevison for your 
advice and words of encouragement. And thank you to my other committee members
Tonia Schwartz and Rita Graze for your valuable input and expertise. 
To my dear friend and labmate, Randy Klabacka, I will always cherish the fond 
memories we created and the enlightening conversations that we've had during our time at Auburn. 
I would also like to acknowledge my other labmates, Matt Buehler,
Saman Jahangiri, Tanner Meyers, Morgan Muell, Claire Tracy, J.R. Wood, 
for making my time at Auburn an enjoyable and enriching experience. 
The stimulating environment created by all of you along with your camaraderie, 
have made my time at Auburn an incredibly enriching and enjoyable experience.
To my parents Mark and Jane and my sister Claire, I am immensely grateful for 
the love, support, and encouragement you have provided me throughout my life. 
I also thank you Mom and Dad for fostering my curiosity for the natural world
from a young age, for being wonderful role models, and for making education
a high priority in my upbringing. 
Lastly, I want to thank my wonderful wife, Aura Cobb, for her unwavering support, love, 
and patience and for the sacrifices you have made for me to accomplish this dream. 
I am profoundly grateful to have you in my life and to have had you by my side 
during this endeavor. 